\documentclass[11pt]{exam}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}

\author{@dantevangelista}

\headrule{}

\begin{document}
\lhead{\textbf{Intro to Math Thinking Fall 2024: Assignment 1}}

\begin{enumerate}[leftmargin=0pt]

\item[1.] 
\begin{itemize}
    \item The man with the telescope saw a woman.
    \item The woman with the telescope saw a man.
\end{itemize}

\item[2.]
\begin{enumerate}[label=(\alph*)]
    \item Sisters reunited in checkout line at Safeway after 10 years.
    \item Large hole appears in High Street. City authorities are investigating it.
    \item Mayor says bus passengers should wear seat belts.
\end{enumerate}

\item[3.] Context: Another meaning is someone without a head injury cannot be ignored \\
\\
Improved: Every head injury cannot be ignored.

\item[4.]
\begin{enumerate}[label=(\alph*)]
    \item Fire could meaning shooting do not use the elevator
    \item Only when there is fire do not use the elevator
\end{enumerate}
Improved: Do not use the elevator in case of building fire.

\item[5.] Not a true statement. \\
Purpose: inform reader of blank page \\
Improved: No content on page.

\item[6.] 
\begin{enumerate}[label=(\alph*)]
    \item Baby on board 
    \item Slow children at play
    \item Pet area
\end{enumerate}

\item[7.] hot is subjective and ambiguous

\item[8.] Suppose $p_1, p_2, ..., p_n$ is the list of all primes. \\
Let $N = (p_1 * p_2 * ... * p_n) + 1$ \\
It is observed, $N > p_n$, then:
\begin{itemize}
    \item If $N$ is prime, there is another prime that continues the list
    \item If $N$ is not prime, it must be divisible by at least 2 primes in the list $p_1, p_2, ..., p_n$
\end{itemize}

\section{FUN}
\item[1.] Context: Punctuation \\
, and ! and ? and . and ; and :

\item[2.] Context: Quotation \\
,, and " or, and ' or << and >>

\end{enumerate}
\end{document}